### 2019-12-03 reports/media/loosely_acc.tex
add interrupts
add soc bounding box

  \node (core2) at (0.4,0.4) [core] {};
  \node (core1) at (0.2,0.2) [core] {};
  \node (core0) at (0,0) [core] {CPU};

@@

@@

>>>>

  \begin{scope}[name=soc, local bounding box=socbb]
  \node (core2) at (0.4,0.4) [core] {};
  \node (core1) at (0.2,0.2) [core] {};
  \node (core0) at (0,0) [core] {CPU};

@@

  \draw[-latex] (hwacc1.west) -- ++(-1,0) node [anchor=south west] {\tiny int};
  \draw[-latex] (hwacc2.west) -- ++(-0.25, 0) -- ++(0, 0.9) -- ++(-2.75, 0) node [anchor=south west] {\tiny int};
  \end{scope}

@@

  \node [fit=(socbb), draw, dashed, rounded corners, thick, inner sep=6pt, label={320:SoC}] {};
